---
title: "Covid-19 Research Project"
subtitle: "Business Analytics Competition 2022<br><br>" 
author: 
  - "Jason Rappazzo"
  - "James Jordon"
  - <br>
date: "April 14, 2022<br><br>"
output: 
  html_document:
    df_print: paged
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: true
    theme: united
    highlight: tango
---

# Project Overview

For our project we have chosen to analyze government COVID-19 related data. As we all know, COVID-19 has impacted just about everyone around the world. Over the past two years, COVID-19 has filled hospitals worldwide and taken countless lives in the process. We want to look at the data to:
<br>
 - Find trends in government responses.
<br>
 - Discover factors that contribute to COVID-19 deaths.
<br> 
 - Explore the reproductive rate of COVID-19.
<br>
 - Look at how the pandemic impacted the growth rates of economies around the world.

<br>

## Data

For our data analysis, we are utilizing data provided by Oxford titled Oxford Covid Government Response Variables. We will also be utilizing data provided by Bloomberg, for which they have created resiliency scores for the 53 top economies in the world. 

```{r, echo=FALSE, collapse=TRUE, warning=FALSE, message=FALSE}
library(readxl)
library(tidyverse)
library(skimr)
library(rstatix)

```

<br>

## Oxford's Data
```{r, collapse=TRUE, warning=FALSE, message=FALSE}
#Path name for the dataset
oxford <- "https://raw.githubusercontent.com/OxCGRT/covid-policy-tracker/master/data/OxCGRT_latest.csv"

#Read csv file
oxford <- read_csv(oxford)
oxford <- rename(oxford, country = CountryName)

rmarkdown::paged_table(oxford)
```

<br>

## Bloomberg's Data
```{r, collapse=TRUE, warning=FALSE, message=FALSE}

#Path name for the dataset
country_info <- "https://covid.ourworldindata.org/data/owid-covid-data.csv"


#Read csv file
country_info <- read_csv(country_info)
country_info <- country_info %>% 
  rename(country = location ) %>% 
  select(country, everything())

rmarkdown::paged_table(country_info)
```

<br>

## Modeling

We plan to build multiple linear regression models and one unsupervised learning method utilizing clustoring. 

The first regression model's dependent variable will be COVID-19 deaths per capita.

The second regression model's dependent variable is the reproductive rate.

The third regression involves the economic impact and our dependent variable will be changes in quarterly GDP.


For all linear regression models, we are in the process of finding proper explanatory variables.


<br>

## Visualizations

We are going to make visualizations using ggplot, plotly, and others to increase the readability of our findings. It is important to become educated on the factors that affect covid deaths in the event another global pandemic becomes present.We hope to display trends that may not be apparently obvious in the hopes that this will aid in the current pandemic and future health problems to come.

# Summary Statistics
```{r, echo=FALSE, collapse=TRUE, warning=FALSE, message=FALSE}
library(readxl)
library(tidyverse)
library(skimr)
library(rstatix)

```


<br>


### Oxford's Summary Statistics
```{r, collapse=TRUE, warning=FALSE, message=FALSE}
rstatix::get_summary_stats(oxford, type = "robust")
```
<br>



### Bloomberg's Summary Statistics
```{r, collapse=TRUE, warning=FALSE, message=FALSE}
rstatix::get_summary_stats(country_info, type = "robust")
```

